---
title: Data Project Proposal
author: Jason Bryer
---

### Data Preparation

```{r setup, echo=TRUE, results='hide', warning=FALSE, message=FALSE}
# load data
library(fivethirtyeight)
library(ggplot2)
data(avengers)
```


### Research question 

**You should phrase your research question in a way that matches up with the scope of inference your dataset allows for.**

Is there a relationship between the number of apperances, years since joining the Avengers, and the Avengers gender?

### Cases 

**What are the cases, and how many are there?**

Each case represents an Avenger.

```{r}
nrow(avengers)
```

### Data collection 

**Describe the method of data collection.**



### Type of study 

**What type of study is this (observational/experiment)?**

Observational



### Data Source 

**If you collected the data, state self-collected. If not, provide a citation/link.**

Five Thirty Eight

https://fivethirtyeight.com/features/captain-america-civil-war-who-would-win/


### Dependent Variable

**What is the response variable? Is it quantitative or qualitative?**

The number of appearances of the Avenger (quantitative)

### Independent Variable

**You should have two independent variables, one quantitative and one qualitative.**

* Years since joining the Avengers (quantitative)
* The Avenger's honary status (qualitative)

### Relevant summary statistics 

**Provide summary statistics for each the variables. Also include appropriate visualizations related to your research question (e.g. scatter plot, boxplots, etc). This step requires the use of R, hence a code chunk is provided below. Insert more code chunks as needed.**

```{r}
summary(avengers$appearances)
sd(avengers$appearances)
psych::describe(avengers$appearances)

psych::describe(avengers$years_since_joining)

table(avengers$honorary)
prop.table(table(avengers$honorary)) * 100

hist(avengers$appearances)

ggplot(avengers, aes(x = years_since_joining, y = appearances, color = gender)) + geom_point()

```

